Building Large-Scale Cross-lingual Knowledge Base from Multi-Encyclopedia

### 2015-06-01 nlpcc/paper.tex
delete algorithm

\section{Result}
\label{sec:result}
\subsection{DataSet}
四个百科的数据统计，包括我们有的百科数据的发布时间，格式（xml。html），article数量，抽取的instance数量，concept数量，property数量, wiki中跨语言链接数量
其实最好有一些我们在抽取过程中删剪的不符合要求的concept或者property数量，不过要看有没有时间再跑一下了
\subsection{Extracted Knowledge Base}
We collect the resources from 4 wiki sites, Enwiki, Zhwiki, Hudong, and Baidu. Each of the wikis has three types of information, which can be utilized for constructing our ontology, namely, specific articles, classification system, and attribute of articles. We extract each raw data, then form the extracted information into well-structured data. Table\ref{tab:extract-result} the result we get after elementary extraction in 4 different wiki sources.

@@

\begin{algorithm}[t]
    \KwIn{ English Infobox template set $TS_{e}$, Chinese Infobox template set $TS_{z}$, English article set $AS_{e}$, Chinese article set $AS_{z}$, existing lan-link map $CL<L_{e}, L_{z}>$ }
\KwOut{Property lan-link map $CL_{p}$}

Initialization: $CL_{p} = \{\} $\\
\ForEach {English Template $T_{e} \in TS_{e}$}{
    $L_{e}$ = label of $T{e}$ \\
    \eIf {$L_{e} \in CL$}{
        $L_{z} = CL\left[L_{e}\right] $ ,\ $T_{z} = TS_{z}\left[L_{z}\right]$\\
        \ForEach{$tl \in T_{e}.pset.tlset \cap T_{z}.pset.tlset $}{
            $CL_{p}$.add(<$T_{e}.p[tl].dl$, $T_{z}.p[tl].dl$>)
        }
    }
}

\ForEach {English Article $A_{e}$ \in $AS_{e}$}{
    $L_{e}$ = label of $A_{e}$
    \eIf {$L_{e} \in CL$}{
        $L_{z} = CL\left[L_{e}\right]$ ,\ $A_{z} = AS_{z}\left[L_{z}\right]$ \\

        $T_{e}$ = Template of $A_{e}$.I ,\ $T_{z}$ = Template of $A_{z}$.I \\

        Set $Cset$ as the Common set of template labels of $T_{e}$ and template labels of $T_{z}$ \\
        $Cset = T_{e}.pset.tlset \cap T_{z}.pset.tlset $ \\

        \ForEach {template label $tl \in Cset $}{
            $CL_{p}$.add(<$T_{e}.pset[tl].dl$, $T_{z}.pset[tl].dl$>)
        }

        \ForEach{English template label $tl_{e} \in T_{e}.pset.tlset \minus Cset$}{
            $p_{e} = T_{e}.pset\left[tl_{e}\right]$ \\
            \ForEach{Chinese template label $tl_{z} \in T_{z}.pset.tlset - Cset$}{
                $p_{z} = T_{z}.pset\left[tl_{z}\right]$ \\
                \eIf {$p_{e}.type$ is datatype $\&\&$ $p_{z}.type$ is datatype}{
                    \eIf {CalculateSimilar($p_{e}.v$, $p_{z}.v$) > $threshold$}{
                        $CL_{p}$.add(<$p_{e}.dl$, $p_{z}.dl$>)
                    }
                } \eElseIf {$p_{e}.type$ is object $\&\&$ $p_{z}.type$ is object}{
                    \eIf{ReferToCommmonEntity($p_{e}.v$, $p_{z}.v$)}{
                        $CL_{p}$.add(<$p_{e}.dl$, $p_{z}.dl$>)
                    }
                }
            }
        }
    }
}
\caption{Property Links Extraction}
\label{alg:ple}
\end{algorithm}

>>>>

\section{Result}
\label{sec:result}
\subsection{DataSet}
四个百科的数据统计，包括我们有的百科数据的发布时间，格式（xml。html），article数量，抽取的instance数量，concept数量，property数量, wiki中跨语言链接数量
其实最好有一些我们在抽取过程中删剪的不符合要求的concept或者property数量，不过要看有没有时间再跑一下了
The English Wikipedia dump files archived in April 2015 contains XXX articles an XXX categories. At the same period, the Chinese Wikipedia dump downloaded has XXX articles and XXX categories. While the Chinese Encyclopedia Baidu Baike we acquired in 2015 has XXX articles and XXX categories. And Hudong Baike in 2014 has XXX articles and XXX categories.

\subsection{Extracted Knowledge Base}
We collect the resources from 4 wiki sites, Enwiki, Zhwiki, Hudong, and Baidu. Each of the wikis has three types of information, which can be utilized for constructing our ontology, namely, specific articles, classification system, and attribute of articles. We extract each raw data, then form the extracted information into well-structured data. Table\ref{tab:extract-result} the result we get after elementary extraction in 4 different wiki sources.

@@
